### 2018-05-07 doc/paper.tex
Finished the a prior bounds proof(s).
Still needed:

- Proof of Lemma 4.2
- Add comment about what the a priori bounds are for small
  values of K
- Use the a priori bounds in my plot (and maybe in the JLCS10
  plot)

As we'll see soon (Lemma~\ref{lemma:k-order}), putting a bound on
sums of the form \(\sum_{j = 0}^k \ell_{F, j}^{(k)} B_{j, k}(s)\) will
be necessary to get an overall bound on the relative error for
\texttt{CompDeCasteljauK}, so we define
\(L_{F, k} \coloneqq \sum_{j = 0}^k \ell_{F, j}^{(k)} B_{j, k}(s)\).

\begin{lemma}\label{lemma:L-and-D-bounds}
For \(s \in \left[0, 1\right]\), the Bernstein-type sum defined above
satisfies the following bound:
\begin{equation}\label{L-sum-bound}
L_{F, n - k} \leq \left[\left(3^F \binom{k}{F - 1} + \bigO{k^{F - 1}}\right)
  \mach^F + \bigO{\mach^{F + 1}}\right] \cdot \widetilde{p}(s).
\end{equation}
In particular, this means that
\(L_{F, k} = \bigO{(3 \mach)^F} \cdot \widetilde{p}(s)\).
\end{lemma}

@@

\begin{lemma}\label{lemma:k-order}
The \(K\)-order error \(\db{K}^{(0)}_0\) satisfies
\begin{equation}
  \left|\db{K - 1}^{(0)}_0 - \cdb{K - 1}^{(0)}_0\right| =
  \left|\db{K}^{(0)}_0\right| \leq \alpha(n) \mach^K
  \widetilde{p}(s).
\end{equation}
\end{lemma}

\begin{proof}
As in \eqref{matrix-de-casteljau}, we can express the compensated
de Casteljau algorithm as
\begin{equation}
\db{F}^{(k)} = U_{k + 1} \db{F}^{(k + 1)} + \ell_{F}^{(k)}
\Longrightarrow \db{F}^{(0)} = \sum_{k = 0}^{n - 1}
U_1 \cdots U_k \ell_F^{(k)} = \sum_{k = 0}^{n - 1}
\left[\sum_{j = 0}^k \ell_{F, j}^{(k)} B_{j, k}(s)\right].
\end{equation}
For the inexact equivalent of these things, first note that
\(\widehat{r} = (1 - s)(1 + \delta)\). Due to this,
we put the \(\widehat{r}\) term at the end of each update step to reduce
the amount of round-off:
\begin{align}
  \cdb{F}_j^{(k)} &=
  \widehat{\ell}_{F, j}^{(k)} \oplus
  \left(s \otimes \cdb{F}_{j + 1}^{(k + 1)}\right) \oplus
  \left(\widehat{r} \otimes \cdb{F}_j^{(k + 1)}\right) \\
&= (1 - s) \cdot \cdb{F}_j^{(k + 1)}(1 + \theta_3) +
  s \cdot \cdb{F}_{j + 1}^{(k + 1)}(1 + \theta_3) +
  \widehat{\ell}_{F, j}^{(k)} (1 + \theta_2) \\
\Longrightarrow \cdb{F}^{(k)} &=
  U_{k + 1} \cdb{F}^{(k + 1)}(1 + \theta_3) +
  \widehat{\ell}_{F}^{(k)} (1 + \theta_2) \\
\Longrightarrow \cdb{F}^{(0)} &=
  \sum_{k = 0}^{n - 1}
  U_1 \cdots U_k \widehat{\ell}_F^{(k)} (1 + \theta_{3k + 2})
  = \sum_{k = 0}^{n - 1}
  \left[\sum_{j = 0}^k \widehat{\ell}_{F, j}^{(k)} (1 + \theta_{3k + 2})
    B_{j, k}(s)\right].
\end{align}
Since
\begin{equation}
\db{F + 1}_0^{(0)} = \db{F}_0^{(0)} - \cdb{F}_0^{(0)} = \sum_{k = 0}^{n - 1}
\sum_{j = 0}^k \left(\ell_{F, j}^{(k)} -
\widehat{\ell}_{F, j}^{(k)} (1 + \theta_{3k + 2})\right) B_{j, k}(s)
\end{equation}
it's useful to put a bound on \(\ell_{F, j}^{(k)} -
\widehat{\ell}_{F, j}^{(k)} (1 + \theta_{3k + 2})\). Via
\begin{align}
\widehat{\ell}_{F, j}^{(k)} &= e_1 \oplus \cdots \oplus e_{5F - 2} \oplus
\left(\rho \otimes \cdb{F - 1}_j^{(k + 1)}\right) \\
&= e_1\left(1 + \theta_{5F - 2}\right) + \cdots +
e_{5F - 2}\left(1 + \theta_2\right) +
\rho \cdot \cdb{F - 1}_j^{(k + 1)} \left(1 + \theta_2\right)
\end{align}
we see that
\begin{equation}
\left|\ell_{F, j}^{(k)} -
\widehat{\ell}_{F, j}^{(k)} (1 + \theta_{3k + 2})\right| \leq
\gamma_{3k + 5F} \cdot \widetilde{\ell}_{F, j}^{(k)}
\Longrightarrow
\left|\db{F + 1}_0^{(0)}\right| \leq \sum_{k = 0}^{n - 1}
\gamma_{3k + 5F} \sum_{j = 0}^k \widetilde{\ell}_{F, j}^{(k)} B_{j, k}(s).
\end{equation}
Since Lemma~\ref{lemma:L-and-D-bounds} (in particular \eqref{L-sum-bound})
tells us that \(\sum_{j = 0}^k \widetilde{\ell}_{F, j}^{(k)} B_{j, k}(s)
= L_{F, k} = \bigO{\mach^F}\) ...
\end{proof}

\begin{theorem}
  If no underflow occurs, \(n \geq 2\) and \(s \in \left[0, 1\right]\)
  \begin{equation}
    \frac{\left|p(s) - \mathtt{CompDeCasteljau}(p, s, K)\right|}{
      \left|p(s)\right|} \leq \left[\mach + \bigO{\mach^2}
      \right] +
      \left[\alpha(n) \mach^K + \bigO{\mach^{K + 1}}\right] \cond{p, s}.
  \end{equation}
\end{theorem}

\begin{proof}
Since
\begin{equation}
\mathtt{CompDeCasteljau}(p, s, K) = \widehat{b}_0^{(0)} \oplus
\cdb{1}_0^{(0)} \oplus \cdots \oplus \cdb{K - 1}_0^{(0)},
\end{equation}
applying Theorem~\ref{thm:sum-k} tells us that
\begin{equation}\label{sum-k-applied}
\left|\mathtt{CompDeCasteljau}(p, s, K) - \sum_{F = 0}^{K - 1}
\cdb{F}_0^{(0)}\right| \leq
\left(\mach + 3 \gamma_{n - 1}^2\right) \left|\sum_{F = 0}^{K - 1}
\cdb{F}_0^{(0)}\right| +
\gamma_{2n - 2}^K \sum_{F = 0}^{K - 1} \left|\cdb{F}_0^{(0)}\right|.
\end{equation}
Since
\begin{equation}
p(s) = b_0^{(0)} = \widehat{b}_0^{(0)} + \db{1}_0^{(0)}
= \cdots
= \widehat{b}_0^{(0)} + \cdb{1}_0^{(0)} + \cdots
+ \cdb{K - 1}_0^{(0)} + \db{K}_0^{(0)}
\end{equation}
we have
\begin{gather}
\left|\sum_{F = 0}^{K - 1} \cdb{F}_0^{(0)}\right|
\leq \left|p(s)\right| + \left|\db{K}_0^{(0)}\right| \quad \text{and} \\
\left|\mathtt{CompDeCasteljau}(p, s, K) - p(s)\right| \leq
\left|\mathtt{CompDeCasteljau}(p, s, K) - \sum_{F = 0}^{K - 1}
\cdb{F}_0^{(0)}\right| +
\left|\db{K}_0^{(0)}\right| \label{triangle-ps}.
\end{gather}
Due to Lemma~\ref{lemma:k-order}, \(\db{F}_0^{(0)} =
\bigO{\mach^F} \widetilde{p}(s)\), hence
\begin{align}
\left(\mach + 3 \gamma_{n - 1}^2\right) \left|\sum_{F = 0}^{K - 1}
\cdb{F}_0^{(0)}\right| &\leq
\left[\mach + \bigO{\mach^2}\right] \left|p(s)\right| +
\bigO{\mach^{K + 1}} \widetilde{p}(s) \\
\gamma_{2n - 2}^K \sum_{F = 0}^{K - 1} \left|\cdb{F}_0^{(0)}\right| &\leq
\gamma_{2n - 2}^K \left|\widehat{b}_0^{(0)}\right| +
\bigO{\mach^{K + 1}} \widetilde{p}(s) \\
&\leq
\gamma_{2n - 2}^K \left[\left|p(s)\right| +
  \bigO{\mach} \widetilde{p}(s)\right] +
\bigO{\mach^{K + 1}} \widetilde{p}(s).
\end{align}
Combining this with \eqref{sum-k-applied} and \eqref{triangle-ps}, we
see
\begin{align}
\left|\mathtt{CompDeCasteljau}(p, s, K) - p(s)\right| &\leq
\left[\mach + \bigO{\mach^2}\right] \left|p(s)\right| +
\left|\db{K}_0^{(0)}\right| +
\bigO{\mach^{K + 1}} \widetilde{p}(s) \\
&\leq
\left[\mach + \bigO{\mach^2}\right] \left|p(s)\right| +
\left[\alpha(n) \mach^K + \bigO{\mach^{K + 1}} \right]
\widetilde{p}(s).
\end{align}
Dividing this by \(\left|p(s)\right|\), we have our result.
\end{proof}

@@

For example, since we have \(r_1(k) = 3 \binom{k}{0}\) we'll have
\(q_1(k) = 3 \binom{k}{1}\). Once this is known
\begin{equation}
r_2(k) = 3 q_1(k - 1) + 5 r_1(k) = 3 \cdot 3 \binom{k - 1}{1} +
5 \cdot 3 \binom{k}{0} = 9 \binom{k}{1} + 6 \binom{k}{0}.
\end{equation}
If we write these polynomials in the ``falling factorial'' basis of
forward differences, then we can show that
\begin{equation}
r_F(k) = 3^F \binom{k}{F} + \cdots
\end{equation}
which will complete the proof. To see this, first note that for a polynomial
in this basis
\(f(k) = A \binom{k}{d} + B \binom{k}{d - 1} + C \binom{k}{d - 2} +
D \binom{k}{d - 3} + \cdots\) we have
\begin{align}
f(k + 1) &= A \binom{k}{d} + (A + B) \binom{k}{d - 1} +
  (B + C) \binom{k}{d - 2} + (C + D) \binom{k}{d - 3} + \cdots \\
f(k - 1) &= A \binom{k}{d} + (B - A) \binom{k}{d - 1} +
  (C - B + A) \binom{k}{d - 2} + (D - C + B - A) \binom{k}{d - 3} + \cdots
\end{align}
Using these, we can show that if
\(r_F(k) = \sum_{j = 0}^{F - 1} c_j \binom{k}{j}\) then
\begin{align}
q_F(k) &= c_{F - 1} \binom{k}{F} + \sum_{j = 1}^{F - 1}
  (c_j + c_{j - 1}) \binom{k}{j} \\
r_{F + 1}(k) &= 3 \left[-c_0 \binom{k}{0} +
  \sum_{j = 1}^F c_{j - 1} \binom{k}{j}\right] +
(5F) \sum_{j = 0}^{F - 1} c_j \binom{k}{j} =
3 c_{F - 1} \binom{k}{F} + \cdots
\end{align}
Under the inductive hypothesis \(c_{F - 1} = 3^F\) so that
the lead term in \(r_{F + 1}(k)\) is \(3 c_{F - 1} \binom{k}{F}
= 3^{F + 1} \binom{k}{F}\).
\end{proof}

>>>>

As we'll see soon (Lemma~\ref{lemma:k-order}), putting a bound on
sums of the form \(\sum_{j = 0}^k \ell_{F, j}^{(k)} B_{j, k}(s)\) will
be useful to get an overall bound on the relative error for
\texttt{CompDeCasteljauK}, so we define
\(L_{F, k} \coloneqq \sum_{j = 0}^k \ell_{F, j}^{(k)} B_{j, k}(s)\).

\begin{lemma}\label{lemma:L-and-D-bounds}
For \(s \in \left[0, 1\right]\), the Bernstein-type sum defined above
satisfies the following bounds:
\begin{align}
L_{F, n - k} &\leq \left[\left(3^F \binom{k}{F - 1} + \bigO{k^{F - 1}}\right)
  \mach^F + \bigO{\mach^{F + 1}}\right] \cdot \widetilde{p}(s) \\
\sum_{k = 0}^{n - 1} \gamma_{3k + 5F} L_{F, k} &\leq
  \left[\left(3^{F + 1} \binom{n}{F + 1} + \bigO{n^F}\right)
  \mach^{F + 1} + \bigO{\mach^{F + 2}}\right] \cdot \widetilde{p}(s).
  \label{L-sum-bound}
\end{align}
In particular, this means that
\(\sum_{k = 0}^{n - 1} \gamma_{3k + 5F} L_{F, k} =
\bigO{(3 n \mach)^{F + 1}} \cdot \widetilde{p}(s)\).
\end{lemma}

@@

\begin{lemma}\label{lemma:k-order}
The \(K\)-order error \(\db{K}^{(0)}_0\) satisfies
\begin{equation}
  \left|\db{K - 1}^{(0)}_0 - \cdb{K - 1}^{(0)}_0\right| =
  \left|\db{K}^{(0)}_0\right| \leq
  \left[\left(3^{K} \binom{n}{K} + \bigO{n^{K - 1}}\right)
  \mach^{K} + \bigO{\mach^{K + 1}}\right] \cdot \widetilde{p}(s).
\end{equation}
\end{lemma}

\begin{proof}
As in \eqref{matrix-de-casteljau}, we can express the compensated
de Casteljau algorithm as
\begin{equation}
\db{F}^{(k)} = U_{k + 1} \db{F}^{(k + 1)} + \ell_{F}^{(k)}
\Longrightarrow \db{F}^{(0)} = \sum_{k = 0}^{n - 1}
U_1 \cdots U_k \ell_F^{(k)} = \sum_{k = 0}^{n - 1}
\left[\sum_{j = 0}^k \ell_{F, j}^{(k)} B_{j, k}(s)\right].
\end{equation}
For the inexact equivalent of these things, first note that
\(\widehat{r} = (1 - s)(1 + \delta)\). Due to this,
we put the \(\widehat{r}\) term at the end of each update step to reduce
the amount of round-off:
\begin{align}
  \cdb{F}_j^{(k)} &=
  \widehat{\ell}_{F, j}^{(k)} \oplus
  \left(s \otimes \cdb{F}_{j + 1}^{(k + 1)}\right) \oplus
  \left(\widehat{r} \otimes \cdb{F}_j^{(k + 1)}\right) \\
&= (1 - s) \cdot \cdb{F}_j^{(k + 1)}(1 + \theta_3) +
  s \cdot \cdb{F}_{j + 1}^{(k + 1)}(1 + \theta_3) +
  \widehat{\ell}_{F, j}^{(k)} (1 + \theta_2) \\
\Longrightarrow \cdb{F}^{(k)} &=
  U_{k + 1} \cdb{F}^{(k + 1)}(1 + \theta_3) +
  \widehat{\ell}_{F}^{(k)} (1 + \theta_2) \\
\Longrightarrow \cdb{F}^{(0)} &=
  \sum_{k = 0}^{n - 1}
  U_1 \cdots U_k \widehat{\ell}_F^{(k)} (1 + \theta_{3k + 2})
  = \sum_{k = 0}^{n - 1}
  \left[\sum_{j = 0}^k \widehat{\ell}_{F, j}^{(k)} (1 + \theta_{3k + 2})
    B_{j, k}(s)\right].
\end{align}
Since
\begin{equation}
\db{F + 1}_0^{(0)} = \db{F}_0^{(0)} - \cdb{F}_0^{(0)} = \sum_{k = 0}^{n - 1}
\sum_{j = 0}^k \left(\ell_{F, j}^{(k)} -
\widehat{\ell}_{F, j}^{(k)} (1 + \theta_{3k + 2})\right) B_{j, k}(s)
\end{equation}
it's useful to put a bound on \(\ell_{F, j}^{(k)} -
\widehat{\ell}_{F, j}^{(k)} (1 + \theta_{3k + 2})\). Via
\begin{align}
\widehat{\ell}_{F, j}^{(k)} &= e_1 \oplus \cdots \oplus e_{5F - 2} \oplus
\left(\rho \otimes \cdb{F - 1}_j^{(k + 1)}\right) \\
&= e_1\left(1 + \theta_{5F - 2}\right) + \cdots +
e_{5F - 2}\left(1 + \theta_2\right) +
\rho \cdot \cdb{F - 1}_j^{(k + 1)} \left(1 + \theta_2\right)
\end{align}
we see that
\begin{equation}
\left|\ell_{F, j}^{(k)} -
\widehat{\ell}_{F, j}^{(k)} (1 + \theta_{3k + 2})\right| \leq
\gamma_{3k + 5F} \cdot \widetilde{\ell}_{F, j}^{(k)}
\Longrightarrow
\left|\db{F + 1}_0^{(0)}\right| \leq \sum_{k = 0}^{n - 1}
\gamma_{3k + 5F} \sum_{j = 0}^k \widetilde{\ell}_{F, j}^{(k)} B_{j, k}(s).
\end{equation}
Applying \eqref{L-sum-bound} directly gives
\begin{equation}
\left|\db{F + 1}_0^{(0)}\right| \leq
  \left[\left(3^{F + 1} \binom{n}{F + 1} + \bigO{n^F}\right)
  \mach^{F + 1} + \bigO{\mach^{F + 2}}\right] \cdot \widetilde{p}(s).
\end{equation}
Letting \(K = F + 1\) we have our result.
\end{proof}

\begin{theorem}
  If no underflow occurs, \(n \geq 2\) and \(s \in \left[0, 1\right]\)
  \begin{multline}
    \frac{\left|p(s) - \mathtt{CompDeCasteljau}(p, s, K)\right|}{
      \left|p(s)\right|} \leq \left[\mach + \bigO{\mach^2}
      \right] + \\
      \left[\left(3^{K} \binom{n}{K} + \bigO{n^{K - 1}}\right) \mach^K +
      \bigO{\mach^{K + 1}}\right] \cond{p, s}.
  \end{multline}
\end{theorem}

\begin{proof}
Since
\begin{equation}
\mathtt{CompDeCasteljau}(p, s, K) = \widehat{b}_0^{(0)} \oplus
\cdb{1}_0^{(0)} \oplus \cdots \oplus \cdb{K - 1}_0^{(0)},
\end{equation}
applying Theorem~\ref{thm:sum-k} tells us that
\begin{equation}\label{sum-k-applied}
\left|\mathtt{CompDeCasteljau}(p, s, K) - \sum_{F = 0}^{K - 1}
\cdb{F}_0^{(0)}\right| \leq
\left(\mach + 3 \gamma_{n - 1}^2\right) \left|\sum_{F = 0}^{K - 1}
\cdb{F}_0^{(0)}\right| +
\gamma_{2n - 2}^K \sum_{F = 0}^{K - 1} \left|\cdb{F}_0^{(0)}\right|.
\end{equation}
Since
\begin{equation}
p(s) = b_0^{(0)} = \widehat{b}_0^{(0)} + \db{1}_0^{(0)}
= \cdots
= \widehat{b}_0^{(0)} + \cdb{1}_0^{(0)} + \cdots
+ \cdb{K - 1}_0^{(0)} + \db{K}_0^{(0)}
\end{equation}
we have
\begin{gather}
\left|\sum_{F = 0}^{K - 1} \cdb{F}_0^{(0)}\right|
\leq \left|p(s)\right| + \left|\db{K}_0^{(0)}\right| \quad \text{and} \\
\left|\mathtt{CompDeCasteljau}(p, s, K) - p(s)\right| \leq
\left|\mathtt{CompDeCasteljau}(p, s, K) - \sum_{F = 0}^{K - 1}
\cdb{F}_0^{(0)}\right| +
\left|\db{K}_0^{(0)}\right| \label{triangle-ps}.
\end{gather}
Due to Lemma~\ref{lemma:k-order}, \(\db{F}_0^{(0)} =
\bigO{\mach^F} \widetilde{p}(s)\), hence
\begin{align}
\left(\mach + 3 \gamma_{n - 1}^2\right) \left|\sum_{F = 0}^{K - 1}
\cdb{F}_0^{(0)}\right| &\leq
\left[\mach + \bigO{\mach^2}\right] \left|p(s)\right| +
\bigO{\mach^{K + 1}} \widetilde{p}(s) \\
\gamma_{2n - 2}^K \sum_{F = 0}^{K - 1} \left|\cdb{F}_0^{(0)}\right| &\leq
\gamma_{2n - 2}^K \left|\widehat{b}_0^{(0)}\right| +
\bigO{\mach^{K + 1}} \widetilde{p}(s) \\
&\leq
\gamma_{2n - 2}^K \left[\left|p(s)\right| +
  \bigO{\mach} \widetilde{p}(s)\right] +
\bigO{\mach^{K + 1}} \widetilde{p}(s).
\end{align}
Combining this with \eqref{sum-k-applied} and \eqref{triangle-ps}, we
see
\begin{align}
& \left|\mathtt{CompDeCasteljau}(p, s, K) - p(s)\right| \\
\leq &
\left[\mach + \bigO{\mach^2}\right] \left|p(s)\right| +
\left|\db{K}_0^{(0)}\right| +
\bigO{\mach^{K + 1}} \widetilde{p}(s) \\
\leq &
\left[\mach + \bigO{\mach^2}\right] \left|p(s)\right| +
\left[\left(3^{K} \binom{n}{K} + \bigO{n^{K - 1}}\right) \mach^K +
\bigO{\mach^{K + 1}} \right]
\widetilde{p}(s).
\end{align}
Dividing this by \(\left|p(s)\right|\), we have our result.
\end{proof}

@@

For example, since we have \(r_1(k) = 3 \binom{k}{0}\) we'll have
\(q_1(k) = 3 \binom{k}{1}\). Once this is known
\begin{equation}
r_2(k) = 3 q_1(k - 1) + 5 r_1(k) = 3 \cdot 3 \binom{k - 1}{1} +
5 \cdot 3 \binom{k}{0} = 9 \binom{k}{1} + 6 \binom{k}{0}.
\end{equation}
If we write these polynomials in the ``falling factorial'' basis of
forward differences, then we can show that
\begin{equation}
r_F(k) = 3^F \binom{k}{F} + \cdots
\end{equation}
which will complete the proof. To see this, first note that for a polynomial
in this basis
\(f(k) = A \binom{k}{d} + B \binom{k}{d - 1} + C \binom{k}{d - 2} +
D \binom{k}{d - 3} + \cdots\) we have
\begin{align}
f(k + 1) &= A \binom{k}{d} + (A + B) \binom{k}{d - 1} +
  (B + C) \binom{k}{d - 2} + (C + D) \binom{k}{d - 3} + \cdots \\
f(k - 1) &= A \binom{k}{d} + (B - A) \binom{k}{d - 1} +
  (C - B + A) \binom{k}{d - 2} + (D - C + B - A) \binom{k}{d - 3} + \cdots
\end{align}
Using these, we can show that if
\(r_F(k) = \sum_{j = 0}^{F - 1} c_j \binom{k}{j}\) then
\begin{align}
q_F(k) &= c_{F - 1} \binom{k}{F} + \sum_{j = 1}^{F - 1}
  (c_j + c_{j - 1}) \binom{k}{j} \\
r_{F + 1}(k) &= 3 \left[-c_0 \binom{k}{0} +
  \sum_{j = 1}^F c_{j - 1} \binom{k}{j}\right] +
(5F) \sum_{j = 0}^{F - 1} c_j \binom{k}{j} =
3 c_{F - 1} \binom{k}{F} + \cdots
\end{align}
Under the inductive hypothesis \(c_{F - 1} = 3^F\) so that
the lead term in \(r_{F + 1}(k)\) is \(3 c_{F - 1} \binom{k}{F}
= 3^{F + 1} \binom{k}{F}\).

For the second inequality, we'll show that
\begin{equation}
\sum_{k = 0}^{n - 1} \gamma_{3k + 5F} L_{F, k} \leq
  \left[q_{F + 1}(n) \mach^{F + 1} +
  \bigO{\mach^{F + 2}}\right] \cdot \widetilde{p}(s)
\end{equation}
and then we'll have our result since we showed above that
\(q_{F + 1}(n) = 3^{F + 1} \binom{n}{F + 1} + \bigO{n^F}\). Since
\(\gamma_{3k + 5F} L_{F, k} \leq (3k + 5F) L_{F, k} \mach +
\bigO{\mach^{F + 1}} \widetilde{p}(s)\) it's enough to consider
\begin{equation}
\sum_{k = 0}^{n - 1} (3k + 5F) r_F(n - k) =
\sum_{k = 1}^n (3(n - k) + 5F) r_F(k).
\end{equation}
Since \(q_F(k) = q_F(k - 1) + r_F(k)\) and \(q_F(0) = 0\) we have
\(q_{F}(n) = \sum_{k = 1}^n r_{F}(k)\) thus
\begin{equation}
q_{F + 1}(n) = \sum_{k = 1}^n r_{F + 1}(k)
= \sum_{k = 1}^n 3 q_F(k - 1) + 5 F r_F(k)
= \sum_{k = 1}^n 3 \left[\sum_{j = 1}^{k - 1} r_F(j)\right] + 5 F r_F(k).
\end{equation}
Swapping the order of summation and grouping like terms, we have our
result.
\end{proof}
